{How do we copy and paste?\\The semantic drift of quotations in blogspace}

### 2014-12-31 brainscopycut.tex
Thank Nico too

We are warmly grateful to Ana Sofia Morais for her precious feedback and advice on this research, and to Jean-Pierre Nadal and Sharon Peperkamp \cam{forgot anyone?} \seb{nope, c'est bon} for useful suggestions and comments.

>>>>

We are warmly grateful to Ana Sofia Morais for her precious feedback and advice on this research, and to Jean-Pierre Nadal, Sharon Peperkamp, and Nicolas Baumard \cam{forgot anyone?} \seb{nope, c'est bon} for useful suggestions and comments.
